Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-04 paper/paper.qmd
Finished introduction

TO REMOVE: The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate [Done]; 2) some detail about what the paper is about [Done]; 3) a clear gap that needs to be filled [Done]; 4) what was done [Done]; 5) what was found; 6) why it is important; 7) the structure of the paper. A reader should be able to read only the introduction and know what was done, why, and what was found. Likely 3 or 4 paragraphs, or 10 per cent of total.

@@

In this paper, to see what factors could impact the likelihood of a homicide case going unsolved, we analyzed data provided by The Washington Post [@datahomicides] that were compiled by their reporters on homicide cases and their status from 2010 to 2017. Previously, The Washington Post has used the data they compiled to construct a map and pinpointing places unsolved homicides occur [@citewashingtonpostmap]. However, specific analysis looking at the differences in case characteristics between specific two US cities like Chicago and Los Angeles has not been done previously. In our findings, it shows that

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

@@

## Areas of improvement and next steps

>>>>

@@

In this paper, to see what factors could impact the likelihood of a homicide case going unsolved, we analyzed data provided by The Washington Post [@datahomicides] that were compiled by their reporters on homicide cases and their status from 2010 to 2017. Previously, The Washington Post has used the data they compiled to construct a map and pinpointing places unsolved homicides occur [@citewashingtonpostmap]. However, specific analysis looking at the differences in case characteristics between specific two US cities like Chicago and Los Angeles has not been done previously. In our findings, it indicates that a majority of unsolved homicide victims from 2010 to 2017 are Black or Hispanic and they are likely to be male but their age does not impact if there case goes unsolved or not. We also found that unsolved homicides are more likely to occur in Chicago compared to Los Angeles from 2010 to 2017. These findings could inform the public and police departments about populations more vulnerable to homicide cases going unsolved and cities to be more alert about such as Chicago with homicide clearance rates.

For the remainder of the paper, the data section [@sec-data] goes over the data we used and its features and limitations, how the dataset was obtained, our variables of interest for our model and preliminary analysis, and a bit of our data cleaning process. In the model section [@sec-model], it discusses the type of model we used, the relationships between variables in our model, and the justification for our model. The results section [@sec-results] contains tables and graphs created based on our data and the results from our model. In the discussion section [@sec-discussion], it goes over what we did in our results, explaining the meaning of our findings, the implications of our findings to the real world, and areas of improvement and suggestions for future works.

@@

## Areas of improvement
